---
title: "data-digital-repression"
author: "Rebecca Strauch"
date: "03/02/2025"
output:
  pdf_document: default
  html_document: default
  word_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Load libraries
```{r, results='asis', warning=FALSE}
rm(list = ls())
library(readr)
library(tidyverse)
library(plyr)
library(countrycode)
library(lubridate)
library(readxl)
library(reshape2)
#remotes::install_github("xmarquez/vdem")
library(vdem)
library(stringr)
library(WDI)
```
Protest data (MMAD v4)
```{r}
mmad <- read.csv("events-v4.csv")

#Only keep anti-government protest.
events <- dplyr::filter(mmad, side == 1)

events$event_date <- as.Date(events$event_date)

serbia <- events %>% filter(cowcode==345)
serbia$cowcode <- "RS"
events <- events %>% filter(!cowcode==345)
events$cowcode <- countrycode(events$cowcode, origin = 'cown', destination = 'iso2c')
events <- rbind(events, serbia)

ru <- events %>% filter(cowcode=="RU")
test <- events %>% 
  dplyr::group_by(year,cowcode) %>%
  dplyr::count()

```

OONI data (Censored websites)
```{r}
ooni <- read.csv("ooni.csv")

###Select only those requests where anomalies were detected 
ooni$anomaly <- ifelse(ooni$blocking==FALSE,FALSE,TRUE)

###Change date
ooni$measurement_start_time <- as.POSIXct(ooni$measurement_start_time, format="%Y-%m-%d")
ooni$date <- format(ooni$measurement_start_time, format="%Y-%m-%d")
ooni$date <- as.Date(ooni$date)

###Create ratio of total requests
###To identify blocked websites, a user sends a request to a number of websites, all within the same probe. Within each probe or individual report, I need at least one accessible website. By this, I can be confident that probes were effective and that not the user had troubles to access the website in general.

ooni <- ooni %>%
  group_by(report_id) %>%
  mutate(any_accessible = any(accessible==TRUE))

###Combine with global list files from Citizen Lab to associate websites
global <- read_csv("global.csv")
names(global)[1] <- "input"

ooni <- left_join(ooni, global, by = "input")

###Filter only relevant data (Human Right Issues etc.)
ooni <- ooni %>%
  dplyr::filter(category_code %in% c("ANON", "HACK", "HOST", "HUMR", "IGO", "LGBT", "MMED",
                            "NEWS", "POLR", "REL", "GRP", "MILX"))

```

OONI data (Censored websites) Only Russia 
```{r}
ooni.rus <- read.csv("ooni.rus.csv")


###Select only those requests where anomalies were detected 
ooni.rus$anomaly <- ifelse(ooni.rus$blocking==FALSE,FALSE,TRUE)

###Change date
ooni.rus$measurement_start_time <- as.POSIXct(ooni.rus$measurement_start_time, format="%Y-%m-%d")
ooni.rus$date <- format(ooni.rus$measurement_start_time, format="%Y-%m-%d")
ooni.rus$date <- as.Date(ooni.rus$date)

###Create ratio of total requests
###To identify blocked websites, a user sends a request to a number of websites, all within the same probe. Within each probe or individual report, I need at least one accessible website. By this, I can be confident that probes were effective and that not the user had troubles to access the website in general.

ooni.rus <- ooni.rus %>%
  group_by(report_id) %>%
  mutate(any_accessible = any(accessible==TRUE))

###Combine with global list files from Citizen Lab to associate websites

ooni.rus <- left_join(ooni.rus, global, by = "input")

###Filter only relevant data (Human Right Issues etc.)
ooni.rus <- ooni.rus %>%
  dplyr::filter(category_code %in% c("ANON", "HACK", "HOST", "HUMR", "IGO", "LGBT", "MMED",
                            "NEWS", "POLR", "REL", "GRP", "MILX"))

```

OONI data (Censored websites) Only Russia 2019
```{r}
ooni.rus.2019 <- read.csv("ooni.rus.2019.csv")


###Select only those requests where anomalies were detected 
ooni.rus.2019$anomaly <- ifelse(ooni.rus.2019$blocking==FALSE,FALSE,TRUE)

###Change date
ooni.rus.2019$measurement_start_time <- as.POSIXct(ooni.rus.2019$measurement_start_time, format="%Y-%m-%d")
ooni.rus.2019$date <- format(ooni.rus.2019$measurement_start_time, format="%Y-%m-%d")
ooni.rus.2019$date <- as.Date(ooni.rus.2019$date)

###Create ratio of total requests
###To identify blocked websites, a user sends a request to a number of websites, all within the same probe. Within each probe or individual report, I need at least one accessible website. By this, I can be confident that probes were effective and that not the user had troubles to access the website in general.

ooni.rus.2019 <- ooni.rus.2019 %>%
  group_by(report_id) %>%
  mutate(any_accessible = any(accessible==TRUE))

###Combine with global list files from Citizen Lab to associate websites

ooni.rus.2019 <- left_join(ooni.rus.2019, global, by = "input")

###Filter only relevant data (Human Right Issues etc.)
ooni.rus.2019 <- ooni.rus.2019 %>%
  dplyr::filter(category_code %in% c("ANON", "HACK", "HOST", "HUMR", "IGO", "LGBT", "MMED",
                            "NEWS", "POLR", "REL", "GRP", "MILX"))

```

Add OONI data (any requests that have been made)
```{r}
ooni_aggr <- ooni %>%
  group_by(date, probe_cc) %>% 
  dplyr::count()%>%
  dplyr::rename(cowcode=probe_cc, any_accessible=n)

ooni_aggr$cowcode <- as.character(ooni_aggr$cowcode)
ooni_aggr$event_date <- as.Date(ooni_aggr$date)

events.all<-left_join(events, ooni_aggr, by=c("event_date", "cowcode"))

events.all <- events.all %>% dplyr::select(!date)

events.all <- events.all %>%
  filter(!cowcode=="RU")

###Only Russia
ooni_aggr <- ooni.rus %>%
  group_by(date, probe_cc) %>% 
  dplyr::count()%>%
  dplyr::rename(cowcode=probe_cc, any_accessible=n)

ooni_aggr$cowcode <- as.character(ooni_aggr$cowcode)
ooni_aggr$event_date <- as.Date(ooni_aggr$date)

events.rus<-left_join(events, ooni_aggr, by=c("event_date", "cowcode"))

events.rus <- events.rus %>% dplyr::select(!date)

events.rus <- events.rus %>%
  filter(cowcode=="RU")

###Russia 2019
ooni_aggr <- ooni.rus.2019 %>%
  group_by(date, probe_cc) %>% 
  dplyr::count()%>%
  dplyr::rename(cowcode=probe_cc, any_accessible=n)

ooni_aggr$cowcode <- as.character(ooni_aggr$cowcode)
ooni_aggr$event_date <- as.Date(ooni_aggr$date)

events.rus.2019<-left_join(events, ooni_aggr, by=c("event_date", "cowcode"))

events.rus.2019 <- events.rus.2019 %>% dplyr::select(!date)

events.rus.2019 <- events.rus.2019 %>%
  filter(cowcode=="RU")



```

Add OONI data to days with and without protest
```{r}
#create empty dataframe on daily basis
data <- expand.grid(seq(as.Date("2016-06-23"), as.Date("2020-10-21"), by = "day"),
                    levels(as.factor(events$cowcode)))
data <- data %>% dplyr::rename(date=Var1, country=Var2)

ooni_aggr_data <- ooni %>%
  filter(anomaly=TRUE) %>%
  group_by(date, probe_cc) %>% 
  dplyr::count()%>%
  dplyr::rename(blocked=n, country=probe_cc)

ooni_aggr_data$blocked <- 1

data <- left_join(data, ooni_aggr_data, by=c("date", "country"))
data$blocked[is.na(data$blocked)] <- 0

events_aggr <- events %>%
  group_by(event_date, cowcode) %>%
  dplyr::count()%>%
  dplyr::rename(protest=n, date=event_date, country=cowcode)
  
events_aggr$protest <- 1
events_aggr$date <- as.Date(events_aggr$date)
  
data <- dplyr::left_join(data, events_aggr, by=c("date", "country"))

data$protest[is.na(data$protest)] <- 0

data$protest[data$protest == 1] <- 'protest'
data$protest[data$protest == 0] <- 'no protest'

data$blocked[data$blocked == 1] <- 'blocked'
data$blocked[data$blocked == 0] <- 'not blocked'

data <- data %>% dplyr::filter(!country=="RU")

table(data$protest, data$blocked)
```


Add only blocked websites
```{r}
ooni_blocked <- ooni %>%
  filter(anomaly==TRUE)

ooni_blocked <- ooni_blocked %>%
  group_by(date, probe_cc) %>% 
  dplyr::count()%>%
  dplyr::rename(cowcode=probe_cc, blocked=n)

ooni_blocked$cowcode <- as.character(ooni_blocked$cowcode)
ooni_blocked$event_date <- as.Date(ooni_blocked$date)

events.all <-left_join(events.all, ooni_blocked, by=c("event_date", "cowcode"))
events.all <- events.all %>% dplyr::select(!date)

###create ratio
events.all$blocked <- ifelse(is.na(events.all$blocked) & !(is.na(events.all$any_accessible)), 0, events.all$blocked)
events.all$ooni_ratio <- events.all$blocked/events.all$any_accessible

events.all$ooni <- ifelse(events.all$ooni_ratio > 0, 1, 0)

```
Add only blocked websites (Russia)
```{r}
ooni_blocked <- ooni.rus %>%
  filter(anomaly==TRUE)

ooni_blocked <- ooni_blocked %>%
  group_by(date, probe_cc) %>% 
  dplyr::count()%>%
  dplyr::rename(cowcode=probe_cc, blocked=n)

ooni_blocked$cowcode <- as.character(ooni_blocked$cowcode)
ooni_blocked$event_date <- as.Date(ooni_blocked$date)

events.rus <-left_join(events.rus, ooni_blocked, by=c("event_date", "cowcode"))
events.rus <- events.rus %>% dplyr::select(!date)

###create ratio
events.rus$blocked <- ifelse(is.na(events.rus$blocked) & !(is.na(events.rus$any_accessible)), 0, events.rus$blocked)
events.rus$ooni_ratio <- events.rus$blocked/events.rus$any_accessible

events.rus$ooni <- ifelse(events.rus$ooni_ratio > 0, 1, 0)

```

Add only blocked websites (Russia, 2019)
```{r}
ooni_blocked <- ooni.rus.2019 %>%
  filter(anomaly==TRUE)

ooni_blocked <- ooni_blocked %>%
  group_by(date, probe_cc) %>% 
  dplyr::count()%>%
  dplyr::rename(cowcode=probe_cc, blocked=n)

ooni_blocked$cowcode <- as.character(ooni_blocked$cowcode)
ooni_blocked$event_date <- as.Date(ooni_blocked$date)

events.rus.2019 <-left_join(events.rus.2019, ooni_blocked, by=c("event_date", "cowcode"))
events.rus.2019 <- events.rus.2019 %>% dplyr::select(!date)

###create ratio
events.rus.2019$blocked <- ifelse(is.na(events.rus.2019$blocked) & !(is.na(events.rus.2019$any_accessible)), 0, events.rus.2019$blocked)
events.rus.2019$ooni_ratio <- events.rus.2019$blocked/events.rus.2019$any_accessible

events.rus.2019$ooni <- ifelse(events.rus.2019$ooni_ratio > 0, 1, 0)

```

```{r}
###Combine
events <- rbind(events.all, events.rus)
events <- rbind(events, events.rus.2019)
```

Add IODA data
```{r}
ioda <- read.csv("~/Documents/digitalrepression/Digital Repression/IODA/ioda_country.csv")

ioda$start <- as_datetime(ioda$start, origin = lubridate::origin)
ioda$start <- as.POSIXct(format(ioda$start, "%Y-%m-%d"))
ioda$date <- as.Date(ioda$start)

ioda_aggr <- ioda %>%
  group_by(date, location_code) %>% 
  dplyr::count() %>%
  dplyr::rename(cowcode=location_code, ioda_number=n)

ioda_aggr$event_date <- as.Date(ioda_aggr$date)

events <- left_join(events, ioda_aggr, by=c("event_date", "cowcode"))
events <- events %>% dplyr::select(!date)
events$ioda_number[is.na(events$ioda_number)] <- 0
events$ioda <- ifelse(events$ioda_number >= 1, 1, 0)
```

Modify physical repression
```{r}
events$physical[events$max_secengagement==0] <- 0
events$physical[events$max_secengagement==1] <- 0
events$physical[events$max_secengagement==2] <- 1
events$physical[events$max_secengagement==3] <- 1

#create year variable in events dataset
events$year <- format(events$event_date, format="%Y")
events$year <- as.numeric(events$year)

```








International NGO Dataset (Kayaalp)
```{r}
library(haven)
INGO <- read_dta("INGO.dta")
INGO <- INGO %>% dplyr::select(Ccode, Year, All_NGO, Global_NGO, National_ngo) %>% filter(Year==2016|Year==2017|Year==2018|Year==2019)

INGO$Ccode <- countrycode(INGO$Ccode, origin = 'cown', destination = 'iso2c')
INGO <- INGO %>% dplyr::rename("cowcode"="Ccode", "year"="Year")

events <- left_join(events, INGO, by=c("cowcode", "year"))
```
 
WDI data
```{r}
wdi <- WDI(country = "all",
      indicator = c("MS.MIL.XPND.GD.ZS", "NY.GDP.PETR.RT.ZS"),
      start = 2016,
      end = 2020)

wdi <- wdi %>%
  dplyr::select(-country, -iso3c)

names(wdi) <- c("cowcode","year", "military", "oil")


events <- left_join(events, wdi, by=c("year", "cowcode"))
```

VDem data
```{r}
vdem <- read_csv("DigitalSocietyProject-v3-CSV/DSP-Dataset-v3.csv")
vdem <- vdem %>% 
  select(country_name, year,v2smgovfilcap_ord, v2smgovshutcap_ord) %>% 
  filter(!year<2016 & !year>2019)  %>% 
  dplyr::rename(cowcode=country_name, filter_cap=v2smgovfilcap_ord, shut_cap=v2smgovshutcap_ord)

vdem$cowcode <- countrycode(vdem$cowcode, origin = 'country.name', destination = 'iso2c')

vdem$year <- as.numeric(vdem$year)
events <- dplyr::left_join(events, vdem, by=c("cowcode", "year"))

```

Export dataset
```{r}
events <- events %>%
  filter(event_date >= '2016-06-23' & event_date <'2020-01-01')
write.csv(events, "df-repression.csv", row.names = FALSE)
```